\titleName{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
started working on architecture section

\section{Architectural Overview} \label{sec:architecture}
\subsection{NVidia Warps}
TODO
Multiple threads are grouped together in "warps"
Thread within a warp are mapped to a vector functional unit (SIMD)
NVIDIA's Maxwell GPUs support up to 64 concurrent warps (2048 threads)
Talk about what a streaming multiprocessor is
Modern unified GPUs consist of multiple streaming multiprocessors (SMs)
  - warp (NVIDIA)/wavefronts (OpenCL)
  - similar to a SIMD processor
  - SM has a warp pool to store context of all running threads
  - HW warp scheduler dispatches and allocates resources
  - large (much larger than a CPU) register file shared across all threads
    - Maxwell architecture has 64K 32-bit registers for each SM
  - kernel: large number of threads executing same piece of code
  - multiple threads form a thread-block; same life-cycle, dispatched together
  - threads within a thread-block (32 or 64) organized into warps
  - warp scheduler schedules a ready warp each cycle, hiding latency of stalled warps
  - CPU launches GPU kernels by dispatching launch commands. Kernel parameters are passed from GPU to CPU at launch time and stored in GPU global memory
  - kernels from different streams are independent and can be run concurrently, but kernels within a stream are sequential
  - see DTBL paper for good intro
  - also see Locality Aware paper for internals of a SM
  - cooperative thread array (CTA) - see Weak behavior paper

\section{Challenges} \label{sec:challenges}
\subsection{Heterogeneous Applications}
TODO
Maximizing resource utilization while minimizing shared resource contention between CPU and GPU is hard
\subsection{Memory Limitations}
TODO

>>>>

\section{Architectural Overview} \label{sec:architecture}
\subsection{Streaming Multiprocessors}
Modern unified GPUs consist of multiple streaming multiprocessors (SMs)
\begin{itemize}
  \item warp (NVIDIA)/wavefronts (OpenCL)
  \item similar to a SIMD processor
  \item SM has a warp pool to store context of all running threads
  \item HW warp scheduler dispatches and allocates resources
  \item large (much larger than a CPU) register file shared across all threads
    \item Maxwell architecture has 64K 32-bit registers for each SM
  \item kernel: large number of threads executing same piece of code
  \item multiple threads form a thread-block; same life-cycle, dispatched together
  \item threads within a thread-block (32 or 64) organized into warps
  \item warp scheduler schedules a ready warp each cycle, hiding latency of stalled warps
  \item CPU launches GPU kernels by dispatching launch commands. Kernel parameters are passed from GPU to CPU at launch time and stored in GPU global memory
  \item kernels from different streams are independent and can be run concurrently, but kernels within a stream are sequential
  \item see DTBL paper for good intro
  \item also see Locality Aware paper for internals of a SM
  \item cooperative thread array (CTA) - see Weak behavior paper
\end{itemize}
\subsection{NVIDIA Warps}
\begin{itemize}
  \item Multiple threads are grouped together in ``warps''
  \item Thread within a warp are mapped to a vector functional unit (SIMD)
  \item NVIDIA's Maxwell GPUs support up to 64 concurrent warps (2048 threads)
\end{itemize}

\section{Challenges of GPGPU} \label{sec:challenges}
\subsection{Heterogeneous Applications}
TODO
Maximizing resource utilization while minimizing shared resource contention between CPU and GPU is hard
\subsection{Memory Limitations}
TODO
